Pool Model

### 2023-12-20 pool_model.tex
compare abm and ode for different setups

    \includegraphics[width=0.49\textwidth]{Figures/snapshot_00000000.png}\hspace{0.02\textwidth}%
    \includegraphics[width=0.49\textwidth]{Figures/snapshot_00006500.png}\vspace{0.02\textwidth}\\
    \includegraphics[width=0.49\textwidth]{Figures/snapshot_00013000.png}\hspace{0.02\textwidth}%
    \includegraphics[width=0.49\textwidth]{Figures/snapshot_00020000.png}%
    \caption{}

@@

    \includegraphics[width=0.7\textwidth]{Figures/abm_ode_comparison.png}
        Comparison of the \ac{abm} and \ac{ode} output corresponding to the parameters presented in table~\ref{tab:spatial_limit_init}.
        % TODO

@@

c1.set_pos(&(old_pos + offset));
c2.set_pos(&(old_pos - offset));
\end{lstlisting}
\caption{
    Sample code for dividing one bacteria cell into two.
}
\end{listing}
%
%
% ................................................................................................
\subsection{Full List of Parameters}
\label{sec:supplement-full-parameters}
\begin{listing}
\begin{lstlisting}[language=json]
{
    "diffusion_constants": [
        15.0,
        15.0
    ],
    "initial_concentrations": [
        2.0,
        0.0
    ],
    "size": 1000.0,
    "n_voxels": null
}
\end{lstlisting}
\caption{
    The \texttt{domain.json} file specifying initial values of the domain.
}
\end{listing}
%
\begin{listing}
\begin{lstlisting}[language=json]
{
    "random_seed": 1,
    "n_times": 20001,
    "dt": 0.5,
    "t_start": 0.0,
    "save_interval": 500,
    "n_threads": 8,
    "show_progressbar": true,
    "save_path": "out/pool_model",
    "save_add_date": true
}
\end{lstlisting}
\caption{
    The \texttt{meta\_params.json} file specifying all parameters not directly related to the simulation content.
    These settings do not represent any model-specific properties but rather generic ones such as time-span or number of threads.
}
\end{listing}
%
\begin{listing}
\begin{lstlisting}[language=json]
{
    "mechanics": {
        "pos": [
        142.85714285714286,
        142.85714285714286
        ],
        "vel": [
        0.0,
        0.0
        ],
        "damping_constant": 0.5,
        "mass": 7.704755982928968
    },
    "cycle": {
        "volume_division_threshold": 14.137166941154069,
        "lag_phase_transition_rate_1": 0.005,
        "lag_phase_transition_rate_2": 0.0025
    },
    "cellular_reactions": {
        "potential_strength": 0.5,
        "food_to_volume_conversion": 0.1,
        "lag_phase_active": true,
        "species": "S1",
        "cell_volume": 7.0685834705770345,
        "uptake_rate": 0.01,
        "inhibition_production_rate": 0.1,
        "inhibition_coefficient": 0.1
    },
    "interactionextracellulargradient": null
}
\end{lstlisting}
\caption{
    The first entry of the \texttt{initial\_cells.json} file which defines every individual particle present in the simulation initially.
}
\end{listing}
%
%
\end{document}

>>>>

    \includegraphics[width=0.49\textwidth]{Figures/abm-homogenous/snapshot_00006000.png}\hspace{0.02\textwidth}%
    \includegraphics[width=0.49\textwidth]{Figures/abm-homogenous/snapshot_00012000.png}\vspace{0.02\textwidth}\\
    \includegraphics[width=0.49\textwidth]{Figures/abm-homogenous/snapshot_00018000.png}\hspace{0.02\textwidth}%
    \includegraphics[width=0.49\textwidth]{Figures/abm-homogenous/snapshot_00024000.png}%
        Simulation snapshots at $1.04$\unit{\day},$2.08$\unit{\day},$3.13$\unit{\day} and $4.17$\unit{\day} corresponding to the parameters given in table~table~\ref{tab:spatial_limit_init}.
        Species $B$ is colored blue while species $A$ is colored in red.

@@

    \begin{subfigure}[c]{0.5\textwidth}
        \includegraphics[width=\textwidth]{Figures/abm-homogenous/abm_ode_comparison.png}
        \subcaption{Homogenous initial cell distribution, $D_R=D_I=30.0$\unit{\micro\metre\squared\per\minute}}
    \end{subfigure}%
    \begin{subfigure}[c]{0.5\textwidth}
        \includegraphics[width=\textwidth]{Figures/abm-homogenous-low-diffusion/abm_ode_comparison.png}
        \subcaption{Homogenous initial cell distribution, $D_R=D_I=5.0$\unit{\micro\metre\squared\per\minute}}
    \end{subfigure}\\
    \begin{subfigure}[c]{0.5\textwidth}
        \includegraphics[width=\textwidth]{Figures/abm-inhomogenous/abm_ode_comparison.png}%
        \subcaption{Inhomogenous initial cell distribution, $D_R=D_I=30.0$\unit{\micro\metre\squared\per\minute}}
    \end{subfigure}%
    \begin{subfigure}[c]{0.5\textwidth}
        \includegraphics[width=\textwidth]{Figures/abm-inhomogenous-low-diffusion/abm_ode_comparison.png}%
        \subcaption{Inhomogenous initial cell distribution, $D_R=D_I=5.0$\unit{\micro\metre\squared\per\minute}}
    \end{subfigure}
        Comparison of the \ac{ode} and \ac{abm} model for different parameter configurations.
        Snapshots of the spatial configurations of cells are included in the appendix~\ref{fig:supplement-spatial-initial-config-cells}.

@@

c1.set_pos(&(old_pos + offset));
c2.set_pos(&(old_pos - offset));
    Sample code for dividing one bacteria cell into two.
\subsection{Full List of Parameters}
\label{sec:supplement-full-parameters}
\begin{lstlisting}[language=json]
{
    "diffusion_constants": [
        15.0,
        15.0
    ],
    "initial_concentrations": [
        2.0,
        0.0
    ],
    "size": 1000.0,
    "n_voxels": null
    The \texttt{domain.json} file specifying initial values of the domain.
\begin{lstlisting}[language=json]
{
    "random_seed": 1,
    "n_times": 20001,
    "dt": 0.5,
    "t_start": 0.0,
    "save_interval": 500,
    "n_threads": 8,
    "show_progressbar": true,
    "save_path": "out/pool_model",
    "save_add_date": true
    The \texttt{meta\_params.json} file specifying all parameters not directly related to the simulation content.
    These settings do not represent any model-specific properties but rather generic ones such as time-span or number of threads.
\begin{lstlisting}[language=json]
{
    "mechanics": {
        "pos": [
        142.85714285714286,
        142.85714285714286
        ],
        "vel": [
        0.0,
        0.0
        ],
        "damping_constant": 0.5,
        "mass": 7.704755982928968
    },
    "cycle": {
        "volume_division_threshold": 14.137166941154069,
        "lag_phase_transition_rate_1": 0.005,
        "lag_phase_transition_rate_2": 0.0025
    },
    "cellular_reactions": {
        "potential_strength": 0.5,
        "food_to_volume_conversion": 0.1,
        "lag_phase_active": true,
        "species": "S1",
        "cell_volume": 7.0685834705770345,
        "uptake_rate": 0.01,
        "inhibition_production_rate": 0.1,
        "inhibition_coefficient": 0.1
    },
    "interactionextracellulargradient": null
    The first entry of the \texttt{initial\_cells.json} file which defines every individual particle present in the simulation initially.
\subsection{Homogenous and Inhomogenous Initial Cell Distributions}
To clarify what we mean by homogenous and inhomogenous initial configurations, we include snapshots of the simulation.
At this point, cells have already grown such that the sizes of cell-clumps are better visible by the naked eye.
The snapshots were taken after $2.08$\unit{\day}.
    \begin{subfigure}[c]{0.5\textwidth}
        \includegraphics[width=\textwidth]{Figures/abm-homogenous/snapshot_00012000.png}
        \subcaption{Homogenous initial cell distribution, $D_R=D_I=30.0$\unit{\micro\metre\squared\per\minute}}
    \end{subfigure}%
    \begin{subfigure}[c]{0.5\textwidth}
        \includegraphics[width=\textwidth]{Figures/abm-homogenous-low-diffusion/snapshot_00012000.png}
        \subcaption{Homogenous initial cell distribution, $D_R=D_I=5.0$\unit{\micro\metre\squared\per\minute}}
    \end{subfigure}\\
    \begin{subfigure}[c]{0.5\textwidth}
        \includegraphics[width=\textwidth]{Figures/abm-inhomogenous/snapshot_00012000.png}%
        \subcaption{Inhomogenous initial cell distribution, $D_R=D_I=30.0$\unit{\micro\metre\squared\per\minute}}
    \end{subfigure}%
    \begin{subfigure}[c]{0.5\textwidth}
        \includegraphics[width=\textwidth]{Figures/abm-inhomogenous-low-diffusion/snapshot_00012000.png}%
        \subcaption{Inhomogenous initial cell distribution, $D_R=D_I=5.0$\unit{\micro\metre\squared\per\minute}}
    \end{subfigure}
        Spatial configuration of cells corresponding to the pictures shown in figure~\ref{fig:spatial-growth-curve}.
    \label{fig:supplement-spatial-initial-config-cells}
\end{document}
